Andres Karjus

### 2019-04-09 index.Rmd
news

<div style="float: left; width: 60%; height: auto; padding-right:10%; overflow: hidden">
<a href="https://andreskarjus.github.io/isle_poster"><IMG SRC="poster_thumbnail.png" ALIGN="left" BR CLEAR="left" style="margin-left:10px; float: right; max-width:20%;" /></a>

>>>>

<div style="float: left; width: 60%; height: auto; padding-right:10%; overflow: hidden">

- Will be teaching an aRt of the Figure series workshop for the Corpus Linguistics in Scotland network this Friday (12.04), titled [Data visualization with R for corpus linguists](https://andreskarjus.github.io/artofthefigure) (if you registred but haven't received the email for some reason, please get in touch!).

- The Language Evolves school workshops are [finished for this year](https://twitter.com/kennysmithed/status/1113456451815661568), with Hermitage Park Primary being the last one. Happy to have been part of it.
